Mixing time of stochastic gradient descent

### 2016-11-13 main.tex
type and related work

\author{Yu Wang, 3031741324}
%\address[label2]{Address Two\fnref{label4}}

@@

Although the problem is interesting, there aren't a lot of schemes availabel to analyzing SGD's mixing time. Traditional ways includs ..... A course book...(Do some survey) However, these methods might not be able to be applied to SGD in a direct way.

@@

Once the mixing time of SGD has been bounded. The second part will dedicated to study the relationship between mixing time and convergence rate. The intuition is that if the corresponding MCMC have a low mixing time, SGD should converge fast. This seems to be a novel perspective to understand SGD. Theoretical analysis as well as empirical experiments will be carried out to further explore this issue. 
\end{abstract}

>>>>

\author{Yu Wang, 3031741324\\ Weixin Cai, 26954913}
%\address[label2]{Address Two\fnref{label4}}

@@

Although the problem is interesting, there aren't a lot of schemes available to analyzing SGD's mixing time. Traditional ways includes ..... A course book...(Do some survey). However, these methods might not be able to be applied to SGD in a direct way.

@@

Once the mixing time of SGD has been bounded. The second part will dedicated to study the relationship between mixing time and convergence rate. The intuition is that if the corresponding MCMC have a low mixing time, SGD should converge fast. This seems to be a novel perspective to understand SGD. Duchi et al.\cite{duchi2012ergodic} shows how the finite-sample convergence rate (expected convergence \& high-probability convergence) of stochastic sub-gradient descent depends on the mixing time of the process. If we can bound the mixing time, subsequently, we will be able to understand the convergence of this class of optimization techniques. Theoretical analysis as well as empirical experiments will be carried out to further explore this issue.
\end{abstract}
